A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-05-03 ms.tex
incremental: everything from Approach to (but not including) Results

\section{Approach}

% XXX incorporate
Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
In this section, we describe how we use PAPER in its imaging configuration
to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
on -45\arcdeg. % XXX

As we've seen above, any one point in the primary beam might be uncertain to 10\% or more. However
this is partially a function of the imaging mode. In \citet{Jacobs:2013p9837} several limitations were identified that
exasperated the primary beam uncertainty.  First, in imaging each source flux is measured at just a few 
points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources.
Here we have averaged over all possible positions making the uncertainty a function of the net uncertainty in the beam,
and stabilizing the source-to-source variations in error bars. The second limitation identified also identified in \citet{Williams:2012p8768}
was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
uncertainty, we weight the source track by an additional factor of the primary beam model.

Algebraically, the apparent flux at alittude-azimuth position $\theta-\phi$,
 is the true flux multiplied by the actual primary beam

\[
S_\textrm{apparent}(\theta,\phi) = B_A(\theta,\phi)  S
\]

Integrating over the full source track and weighting by our model primary beam, we estimate the spectrum

\begin{align}
S_\textrm{estimate} &=& \sum_t   \frac{\sum_\phi B_M(\theta,\phi) S_\textrm{apparent}(\theta,\phi) }{ \sum_\phi B^2_M(\theta,\phi)}
S_\texrm{estimate} & =&  \frac{\sum_\phi B_M(\theta,\phi) B_A(\theta,\phi)}{ \sum_\phi B^2_M(\theta,\phi)} S
\end{align}
In the fully general case, an incompletely sampled track will have its own unique weight. In this case, where each track is fully sampled,
 the only remaining independent variable is the source declination.
\[
g(\delta) = \frac{\sum_\phi B_M(\theta,\phi) B_A(\theta,\phi)}{ \sum_\phi B^2_M(\theta,\phi)}
\label{eq:g}
\]

 \begin{figure}[htbp]
\begin{center}
\includgraphics[width=0.9\textwidth]{plots/model_weighted_beam_sim_track.png}
\caption{\label{fig:beam_track_sim} Simulated model weighted beam track. }
\label{default}
\end{center}
\end{figure}

  \begin{figure}[htbp]
\begin{center}
\includgraphics[width=0.9\textwidth]{plots/model_weighted_beam_sim_track.png}
\caption{\label{fig:beam_track_sim} Simulated model weighted beam track. }
\label{default}
\end{center}
\end{figure}
 We may simulate this integral by calculating $g$ for 
similar, but not identical models. For example, consider the case where the true beam is the model beam 
but rotated by 90 degrees ('y' instead of 'x').  As shown in Figure \ref{XXX}
 tracks separated by 10\arcdeg declination differ by as much as 25\%. 
However, looking at the weighted tracks, the portion inside the sum in Eq \ref{eq:g} (Figure \ref{fig:beam_track_sim}), 
we see that  we see that over a good portion of the beam, these tracks are very similar.  Thus
  the sum displays very little declination dependance (Figure \ref{XXX}), varying by a maximum of 0.7\% over 
  the declination range -30 to -60. 
   However this conclusion is limited by the accuracy of the simulation. To limit our susceptibility to possibly larger errors we limit our use of this
  technique to with $\pm5$\arcdeg of Pictor A.

Another implication of this simulation is that there will be a net bandpass common to each source. 
We estimate this bandpass by nominating one source as a bandpass calibrator, dividing its integrated spectrum by a 
spectral model, and applying these calibration coefficients to the rest of the sources. Note that this  
only puts the measurements on a common flux scale within the PAPER band given the flux model
chosen for the calibrator.  A flux scale extrapolated from many catalog values is calculated separately in \S \ref{sec:flux_scale}.

%This limitation in declination allows us to use a single source to calibrate all the measurements without 
%needing to transfer gain solutions across the sky using a beam model. By insisting that the tracks of all sources
% overlap entirely with a common calibrator we are able to directly calibrate out the effective passband of
% the primary beam. 
%This allows us to make a more precise flux measurement that provides a reference standard for future work.

@@

The spectra reported here are measured by beam-forming, phasing the visibilities to
the target location, and summing to produce a dynamic spectrum. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  Though we do not rely on
the primary beam model to estimate flux, we do employ it here to down weight low SNR measurements.
Each source track is paired with samples of a calibrator to build a calibrator spectrum with the same weighting
and the same track through the primary beam.  This calibrator observation provides a spectral bandpass unique 
to that particular cut through the beam.
The expectation is that, since all sources at similar declinations follow similar tracks 
through the PAPER beam, any errors present in the original measured spectra as a result of differences between
the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
should be corrected by the applied gain factor.

To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
weights derived from a model of
PAPER's primary beam response as an effective approximation of inverse-variance weighting
\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
represents a best estimate given the limitations of the beam model and flux calibration that were established
up to this point, according to the equation:
% XXX equation for time-dependent beam amplitude times source flux for perceived flux density
To further improve these estimates, we derive an additional frequency-dependent gain parameter,
smoothed on 10-MHz scales,
that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum
that represents the best fit to measurements below 1 GHz.
This additional gain factor was applied to all measured spectra, including that
of Pictor A.

Finally,
an absolute flux scale is set
by Monte Carlo fitting to a subset of sources, all of which are calibrated to
the Baars et al scale. 
% XXX elaborate on this, more on Baars, less on MC

@@

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/antpos.png}
\caption{Antenna position in the 64-antenna, minimum-redundancy PAPER array configuration at the Karoo Radio Observatory site in South Africa used for these observations.
% XXX add brief summary of observations.
}\label{fig:antpos}
\end{figure*}

@@

@@

% XXX time-dependent calibration is critical.  modify paragraph below
Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  A predicted gain profile was drived using coefficients characterized in
laboratory measurements \citep{parashare_bradley2009} and
confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
during these observations, the cable temperature was assumed to be the same as the measured balun temperature.

@@

% XXX incorporate
To measure the spectrum of each source, we begin by applying per-antenna phase and gain
calibrations established via self-calibration.  We next remove
the known dependence of amplifier gain and cable attenuation on ambient temperature 
using measured temperature data and temperature coefficients that were characterized in
laboratory measurements \citep{parashare_bradley2009} and confirmed 
in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
osition
and sum over 
all baselines greater than 20 wavelengths in length.
A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
is applied to the resulting
beam to suppress beam sidelobes where sources introduce variations that deviate more than 
$\pm$0.1 mHz from the fringe rate of the source in question.

@@

Spectral time-series are computed by beam-forming to the selected sky
locations. A beam is formed by phasing baselines to the desired location and
summing over baselines.  
%Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.   By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot.

@@

 These complex spectra are then delay-delay rate filtered to remove spectrally
smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR
de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent
spectrum. This is then averaged in time,  weighting by a model of the primary
beam. This down-weighting, or multiplying by the primary beam, should be
clearly distinguished from up-weighting, which we are at pains to avoid.
Weighting by another factor of the primary beam is an effective approximation
of inverse-variance weighting \citep{Pober:2012p8800} and reduces the
contribution of noisy low elevation measurements.  The result is equivalent to
a very long earth rotation synthesis image with a single image pixel. When
combined with the filtering it is a robust and simple method for measuring
spectra of unresolved sources.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/PicA_Oct2011_uv_coverage.png}
\caption{The effective uv coverage, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
% XXX unclear whether amplitudes include our model of Pic A, or are even actual data vs. weights
\end{figure}

The beam-forming method assumes the target is a point source. Our primary
target, Pictor A, is slightly resolved by PAPER, and merits closer attention.
Pictor A is a double-lobed radio galaxy with a main lobe separation of
7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by
PAPER's 15\arcmin synthesized beam. However, given the high SNR of the
observations, resolution effects are observers, in a slight decrease in flux on
the longest ($\sim$300m) baselines. We account for this by weighting baselines
in the beam form step according to a model of structure observed by
\citet{Perley:1997p9312} at 330MHz, which they found to be consistent with
their more limited 74MHz images as well as the detailed high frequency maps.
The normalized image is Fourier transformed and sampled at the desired uv
spacing by spline interpolation. These samples are used to weight each baseline
contribution in the baseline sum. The result is an estimate of the total
integrated flux for Pictor A. Where the resolution is highest, at the top of
the band, the correction is 3\%. At the bottom of the band, where the
resolution size has grown to 19\arcmin, the correction is only 0.6\%. The
resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.

% XXX specific discussion of baseline weights to compensate for resolution effects for Pictor A
% XXX need to elaborate on correcting for resolution effects for PicA.
% XXX check paragraph below for relavant phrases
Because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.

\begin{figure}
\includegraphics[width=0.96\textwidth]{plots/picA_Perley.png}
\caption{
Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}. Black circle
indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To
correct for the small residual structure in the PAPER measurements we
interpolated the PAPER baselines in the uv plane. At the highest frequency this
% XXX "interpolated" needs to be clarified
led to a 3\% correction, at the lowest frequency, 0.6\%.
\label{fig:pic_perley}}
\end{figure}

@@

% XXX selection of calibrator sources

The gain of each channel is the product of an overall instrumental passband and
the spectral dependence of the primary beam in the direction of the source.
Sources sharing the same track through the primary beam will have the same
average spectral gain function resulting from frequency dependent primary beam
attenuation.   We matched each measured source spectrum time sample to the
nearest sample (in altitude/azimuth) of a calibrator source
(J2331-416)\footnote{This source was chosen for the amount of data found in the
literature and the apparent smoothness of the spectrum.}.  We then, average the
% XXX clarify why one source used here, and more sources later 
two matched data streams in time.  Since both tracks make the same slice
through the primary beam, they will have the same average effective gain.
Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
% XXX forward reference section on fitting spectra for how this was derived for 2331
bandpass gain.  After calibrating the raw 203 channel spectra with this
bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
the standard deviation as an estimate of the error.

@@

% XXX write this

To compare with observations at other frequencies we must assume a spectral
model. The prevailing spectral model for low frequency radio sources is a
single power law due to synchrotron emission, though curvature or other
deviation from a power-law is not-uncommon.   To establish a baseline model, we
fit a spectral model to prior catalog data from the spectrally and spatially
cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method
described in \S \ref{sec:flux_scale} and the Appendix. Confidence contours for
these fits are shown in grey in Figs. \ref{fig:SI_contour_1} -
\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
precision, as the Vollmer catalog emphasizes minimization of cross-match error
but at the cost of excluding data points.  The fit is then performed again with
both PAPER and catalog data, shown in black on the same Figures. The values are
given in Table \ref{tab:fits}, and
illustrated in Figure \ref{fig:src_spec}.

In this paper we estimate spectral model parameters and flux calibration in a
Bayesian way by calculating and marginalizing the posterior probability of the
data, past and present, given a spectral and instrumental model.   This method
offers improved repeatability by specifying a single objective function that
represents the quality of the model fit and naturally defines the errors on the
parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or
\citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
astrophysical example by \cite{Press:1997p9783}.

% XXX paragraph too remedial. digest
In general an experiment measures data $D$ and given some model of the
statistics of the measurement one usually assigns an error bar defining the
probability of getting that data, given a model $M$.  Given all the new data,
and prior data, there will be a new optimal set of model parameters $M$ with
associated error bars.  In general, these error bars are a parameterization of
a probability distribution function.  The pdf associated with the data often
called the likelihood ($\mathcal{L}$), while the one corresponding the model
error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
are related

\[
\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
\] 
by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
$M$ (given past experiments) over the normalization factor, integrating over
all models.  In general the posterior pdf depends on both the known relation
between the model parameters and as well as correlations hidden within the
data.

% XXX too remedial.  digest to 1 senetence
Direct calculation of the posterior is difficult, particularly the
normalization factor, however there is a simple procedure for drawing samples
from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
Given any current location in parameter space, this algorithm draws a new set
of parameters and computes the relative likelihood increase. If the probability
difference is larger than a number drawn randomly from the set $(0:1]$, the
jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
such steps, this process has been shown to converge on the true posterior
distribution.  In practice it is run for a large number of steps until things
appear to stabilize. The best fit model is the median of all the sampled
parameter sets, while the volume containing a well defined fraction of samples
sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
corresponding to a gaussian distribution contains 65\% of the samples. In
practice the contours are not gaussian. Here we choose a slightly more
conservative probability level of 76\%

We fit a spectral power law to catalog values by sampling
a (log) likelihood which assumes Gaussian measurement errors

\[
\logL = \sum_\nu{\frac{\left(S_\nu - S150\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta \textrm{SPAPER}_\nu}} \label{eq:catlogL}
\]

@@

\begin{figure}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
\caption{
A more detailed view of the posterior probability distribution. On the left
Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
As above, grey for  the fit to catalog data, black for joint catalog and PAPER
fit.
}
\end{figure}

At this stage each source flux is tied to a model fit on the catalog values of
J2331-416. The accuracy of this fit and the implied uncertainty in the flux
scale limits the accuracy of the PAPER measurements..  To refine the flux
scale, we bootstrap a single global flux scale correction factor using 5
sources selected for their brightness, spectral linearity and data
availability\footnote{Calibration sources:
2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
spectral model we go beyond the data found in SPECFIND, using all spectral
measurements below 2GHz found in the NED database.  These catalog measurements
are primarily by Parkes, and Molonglo with the best precision coming from the
Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
given, we assume uncertainty of 25\%.

As described in the Appendix, we fit spectral index models for all sources
(using catalog data) simultaneously with a global PAPER flux scale factor
(using the PAPER data). We fit the model using a Markov Chain Monte Carlo
sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and
catalog values ($Scat_{\nu}$) given a spectral index model for each source and
a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
The resulting flux scale distribution function is shown in Figure
\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
multiplicative error on every calibrated PAPER measurement.

>>>>

\section{Approach}
\label{sec:approach}
% XXX incorporate
Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
In this section, we describe how we use PAPER in its imaging configuration
to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
on -45\arcdeg.

 In \citet{Jacobs:2013p9837} several limitations were identified that
exasperated the primary beam uncertainty.  First, in imaging each source flux is measured at just a few 
points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources.
Here we have averaged over all possible positions making the uncertainty a function of the net uncertainty in the beam,
and stabilizing the source-to-source variations in error bars. The second limitation, identified in \citet{Williams:2012p8768},
was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
uncertainty, we weight the source track by an additional factor of the primary beam model.

As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. Each source track
provides a detailed measurement of the primary beam relative to the peak of the measured flux. However,
a model $g(\delta)$ is still required to calibrate between declinations. This model will be effective over a range of declinations, but will diverge at
some rate depending on the accuracy of the slope of the beam model, limiting our declination range ($\Delta \delta$).

EQUATION FOR BEAM ERROR %XXX
% \[
% g(\alpha,\delta) = \frac{d B(\theta,\phi)}{d\delta} \Delta \delta 
% \]
Using our source tracks, we can measure the slope of the beam and compare with models over a range of angles

EQUATION FOR BEAM ERROR ALONG SOURCE TRACK %XXX

As we see in Figure XXX the model beam is able to predict the measured beam slope across a 5\arcdeg
distance to within XXX\%.

\[
B_M = B_M(\theta(t),\phi(t))\\
\sim 0.02\\
\Delta B /B_M= \Delta (S_p)/B^2_M \sim \Delta B_M \\
(\Delta B - \Delta B_M)/B_M < 0.01
\]

@@

The spectra reported here are measured by beam-forming, phasing the visibilities to
the target location, and summing to produce a dynamic spectrum. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time average is 
weighted by an additional factor of the PAPER's primary beam response 
\citep{pober_et_al2012}.  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M}\\
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S\\ \label{eq:g}
\end{align}

which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
sources at the same declination, and as we found above, diverges slowly from the model in the 10\arcdeg declination stripe.
We estimate this spectral dependent gain for a calibrator (J2331-416) fitting a spectral index model to the
 well-defined data points below 2GHz. This removes an overall offset.

 Finally we average the spectra from a resolution of 400kHz to 10MHz bins, taking the standard deviation within these bins
 for an estimate of the uncertainty.

At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
they must be put on a global flux scale. We also have only a limited estimate of our error from our intra-channel
rms.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
have all been set, as best as possible, to the Baars et al scale.  Using a Bayesian analysis we compute the 
variation in the flux scale implied by comparing many sources to prior catalog. By including sources from across
the declination range,the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
or prior catalog uncertainty.  So though the final scale is calibrated to the Baars scale as extrapolated beyond its
defined band, the error on the flux scale fully encapsulates the error resulting from this extrapolation.

@@

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/antpos.png}
\caption{Antenna position in the 64-antenna, minimum-redundancy PAPER array configuration at the Karoo Radio Observatory site in South Africa used for these observations.
Data was captured during July and October of 2011 on a single 'x' polarization over a band between 120 and 180 MHz.
}\label{fig:antpos}
\end{figure*}

@@

%I'm Confused.  These are describing a different ordering of steps. Must re-read compression script.

@@

% XXX time-dependent calibration is critical.  modify paragraph below

Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  A predicted gain profile was derived using coefficients characterized in
laboratory measurements \citep{parashare_bradley2009} and
confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
during these observations, the cable temperature was assumed to be the same as the measured balun temperature.

@@

% XXX incorporate
%To measure the spectrum of each source, we begin by applying per-antenna phase and gain
%calibrations established via self-calibration.  We next remove
%the known dependence of amplifier gain and cable attenuation on ambient temperature 
%using measured temperature data and temperature coefficients that were characterized in
%laboratory measurements \citep{parashare_bradley2009} and confirmed 
%in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
%osition
%and sum over 
%all baselines greater than 20 wavelengths in length.
%A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
%is applied to the resulting
%beam to suppress beam sidelobes where sources introduce variations that deviate more than 
%$\pm$0.1 mHz from the fringe rate of the source in question.

@@

Spectral time-series are computed by beam-forming to the selected sky
locations. A beam is formed by phasing baselines to the desired location and
summing over baselines longer than 20 wavelengths.
%Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.   By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot.

@@

 These complex spectra are then fringe rate filtered to remove spectrally
smooth sources that deviate more than $\pm$0.1mHz from the fringe rate of the source in question
 \citep{Parsons:2009p7859} (cf the LOFAR
de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent
spectrum with minimal side lobes. This is then averaged in time,  weighting by a model of the primary
beam as discussed above.
The result is equivalent to
a very long earth rotation synthesis image with a single image pixel. The weighted
contributions from each baseline are shown in Figure \ref{fig:uv_coverage}.When
combined with the filtering it is a robust and simple method for measuring
spectra of unresolved sources.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/PicA_Oct2011_uv_coverage.png}
\caption{The effective uv coverage of a 10MHz-wide spectrum bin, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
Not shown here are the weights interpolated from the Perley et al 330MHz map (Fig. \ref{fig:pic_perley}) used to recover the total integrated flux of Pic  which represent a few \% change on the longest baselines.
\end{figure}

The beam-forming method assumes the target is a point source. Our primary
target, Pictor A, is slightly resolved by PAPER, and merits closer attention.
Pictor A is a double-lobed radio galaxy with a main lobe separation of
7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by
PAPER's 15\arcmin synthesized beam. However, given the high SNR of the
observations, we see a 20\% drop in flux on the longest ($\sim$300m) baselines. 
We account for this by weighting baselines
in the beamform step according to a model of structure observed by
\citet{Perley:1997p9312} at 330MHz, which they found to be consistent with
their more limited 74MHz images as well as the detailed high frequency maps.
The normalized image is Fourier transformed and sampled at the desired uv
spacing by spline interpolation. These samples are used to weight each baseline
contribution in the baseline sum. The result is an estimate of the total
integrated flux for Pictor A. Where the resolution is highest, at the top of
the band, the correction is 3\%. At the bottom of the band, where the
resolution size has grown to 19\arcmin, the correction is only 0.6\%. The
resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.

\begin{figure}
\includegraphics[width=0.96\textwidth]{plots/picA_Perley.png}
\caption{
Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}. Black circle
indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To
correct for the small residual structure in the PAPER measurements we resampled
the Perley image to the PAPER resolution and estimated the relative contribution
 to each PAPER baseline.  At the highest frequency this
led to a 3\% correction, at the lowest frequency, 0.6\%.
\label{fig:pic_perley}}
\end{figure}

@@

The resulting set of spectra were then calibrated to a model of J2331-416 to remove 
the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} fit to measurements beolow 1GHz \citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.}
was selected for its relatively high brightness, spectral smoothness and large quantity
 of available catalog data. Each source track has a slightly different sample profile
 resulting from different amounts of flagged data at each time and channel. To account
 for these differences in the bandpass calibration we build a set of calibration tracks 
 that match the tracks for each source. Calibration of each source then proceeds with
 an optimally matched calibration spectrum.

%The gain of each channel is the product of an overall instrumental passband and
%the spectral dependence of the primary beam in the direction of the source.
%Sources sharing the same track through the primary beam will have the same
%average spectral gain function resulting from frequency dependent primary beam
%attenuation.   We matched each measured source spectrum time sample to the
%nearest sample (in altitude/azimuth) of a calibrator source
%(J2331-416)\footnote{This source was chosen for the amount of data found in the
%literature and the apparent smoothness of the spectrum.}.  We then, average the
%% XXX clarify why one source used here, and more sources later 
%two matched data streams in time.  Since both tracks make the same slice
%through the primary beam, they will have the same average effective gain.
%Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
%% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
%% XXX forward reference section on fitting spectra for how this was derived for 2331
%bandpass gain.  After calibrating the raw 203 channel spectra with this
%bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
%the standard deviation as an estimate of the error.

@@

There is a variety of prior data at multiple wavelengths to which we want to calibrate
and then compare our measurements.  Our method for doing both of these steps
is to assume a basic spectral model relating the different catalog data points and
fit for spectral model and gain parameters.

We estimate spectral model parameters and flux calibration in a
Bayesian way by calculating and marginalizing the posterior probability of the
catalog and new PAPER data.   This method
offers improved repeatability by specifying a single objective function that
represents the quality of the model fit and naturally defines the errors on the
parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or
\citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
astrophysical example by \cite{Press:1997p9783}. In brief, measurement errors
are related to parameter model errors via the likelihood, which we can calculate, 
and the posterior, which we cannot.  However, the posterior is theoretically
well sampled by a Markov Chain Monte Carlo sampler, which selects parameter
values at random, computes the likelihood of the model given the data and noise model,
and accepts or rejects the step based on an outside decision factor unrelated to the data.

Here we use the emcee sampler by \citet{Mackay:2003p9717} et al to generate chains of
parameter values. The best fit model is the median of all the sampled
parameter sets, while the volume containing a well defined fraction of samples
sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
corresponding to a gaussian distribution contains 65\% of the samples. In
practice the contours are not gaussian. Here we choose a slightly more
conservative probability level of 76\%

To model the relationship between different wavelengths we assume a single spectral index
which is the prevailing spectral energy distribution at low frequencies, 
though curvature or other
deviation from a power-law is not-uncommon.

When fitting models to the full catalog, we use the Vollmer et al
catalog which has been optimally cross-matched at the expense of excluding more data points.
Meanwhile, the gain fit used a small sample of
sources with spectra which meet our calibration criteria: more precision data available,
brighter than most sources in the sample and far from any possibly confusing areas of
the sky. 
By limiting ourselves to a small number of sources we are able to go include catalog points by hand,
to avoid making the error of falsely including erroneously matched 
data points but benefiting from some measurements not included.

At the output of the beam forming and bandpass calibration step, the flux scale
 is tied to a model fit tp the catalog values of
J2331-416. The accuracy of this fit, and the implied uncertainty in the flux
scale, limits the accuracy of the PAPER measurements..  To refine the flux
scale and estimate our flux scale uncertainty, we bootstrap a single global flux scale 
correction factor using 5
sources selected for their brightness, spectral linearity and data
availability\footnote{Calibration sources:
2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
spectral model we go beyond the data found in Vollmer et al, including all spectral
measurements below 2GHz found in the NED database \footnote{\url{ned.ipac.caltech.edu}: Accessed 1 April 2013}.  These catalog measurements
are primarily by Parkes, and Molonglo with the best precision coming from the
Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
given, we assume uncertainty of 25\%.

Using the MCMC method we fit spectral index models to the catalog fluxes
 simultaneously with a global PAPER flux scale factor using  an MCMC chain to calculate the log likelihood

\begin{align}
\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
\end{align}

which samples the posterior probability of PAPER data ($SPAPER_{\nu}$) and
catalog values ($Scat_{\nu}$) given a spectral index model for each source and
a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
Marginalizing over the fitted flux scales, we find the resulting flux scale distribution function which is shown in Figure
\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
multiplicative error on every calibrated PAPER measurement.  These errors are added, in quadrature,
to the errors in the PAPER spectra.

These calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  The
resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
at 185MHz. At least half of this error is due to uncertainty in the flux scale.

\subsection{Fitting Spectral Models}
\label{sec:fitting_models}

Finally we compare all of our  calibrated spectra to catalog measurements. Our method
will be to first establish a best fit model to existing data, then add the PAPER data
to the fit, and assess the degree to which the PAPER data is supported by prior measurements, or the reverse
the degree to which PAPER offers an improvement in our knowledge of the spectrum.

 To establish the baseline model, we
fit a spectral model to catalog data from the spectrally and spatially
cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the
 (log) likelihood which assumes Gaussian measurement errors

\[
\logL = \sum_\nu{\frac{\left(S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta S_\nu} \label{eq:catlogL}
\]

@@

Confidence contours for
the complete set are shown in grey in Figs. \ref{fig:SI_contour_1} -
\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
precision, as the Vollmer catalog emphasizes minimization of cross-match error
but at the cost of excluding data points.  The fit is then performed again with
both PAPER and catalog data, shown in black on the same Figures. The values are
given in Table \ref{tab:fits}, and
illustrated in Figure \ref{fig:src_spec}.
